A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-06-08 paper/paper.tex
Work on the experiments
Minor changes... Further work tomorrow.

The comparisons were on average across different drawings with same number of vertices. For Properties~P.\ref*{p:cr-res}, P.\ref*{p:to-res} and P.\ref*{p:an-res}, we further adjusted each of the algorithms of the experiment to optimize the corresponding measures. Then, for each of them we reported the average of the corresponding aspect ratios and number of crossings of the produced layouts. Note that all algorithms of the experiment can easily be adjusted to maximize only the crossing resolution, or only the angular resolution or both (by maximizing the total resolution). In our algorithm, this can be achieved by adjusting appropriately the content of the vertex-pool (as we saw in Section~\ref{ssec:variants}), while in the algorithms of Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13} and of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13} by switching on only the forces that maximize the corresponding measured properties (note that, each of these two algorithms has a different set of forces to maximize the crossing and the angular resolution, such that together they maximize the total resolution).

\myparagraph{Crossing resolution} Our results for the crossing resolution are summarized in Fig.~\ref{fig:cr-res}. Here, each algorithm was adjusted so to maximize exclusively the crossing resolution (i.e., by ignoring the drawing's angular resolution). It is immediate to see that our algorithm outperforms all other ones in terms of the crossing resolution of the produced drawings, when we do not impose any restriction on the aspect ratio of the computed drawings; refer to the solid-black curve, denoted as \emph{unrestricted}, in Fig.~\ref{fig:cr-res-1}. The variant of our algorithm, which does not violate the aspect ratio of the initial layout, leads to drawings with slightly smaller crossing resolution; refer to the solid-gray curve, denoted as \emph{ar-restricted}, in Fig.~\ref{fig:cr-res-1}. Finally, the two force-directed algorithms seem to produce drawings with worse crossing resolution; refer to the dotted-black and dotted-gray curves of Fig.~\ref{fig:cr-res-1}.

While our unrestricted algorithm produces drawings of better crossing resolution, this seems to come at a cost of increased aspect ratio (see Fig.~\ref{fig:cr-res-2}), which, however, is still better that the corresponding aspect ratio of the drawings produced by the algorithm of Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13}. For the latter algorithm, it seems that the forces due to angles formed at the crossings outperform the corresponding spring forces, which try to keep the lengths of the edges short. Going back to our unrestricted algorithm, its behaviour is up to a certain degree expected mainly due to the fact that there is no control on the lengths of the edges.
% (as it is, e.g., in the case of the force-directed algorithm of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13}, whose sping forces inpose stong restrictions on the edge lengths). 
On the other hand, the restricted variant of our algorithm, which does not allow the aspect ratio to decrease, has more or less comparable performace (in terms of the aspect ratio of the computed drawings) as the one of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13}.

>>>>

The reported results are on average across different drawings with same number of vertices. For Properties~P.\ref*{p:cr-res}, P.\ref*{p:to-res} and P.\ref*{p:an-res}, we further adjusted each of the algorithms of the experiment to optimize exclusively the corresponding measures. Then, for each of them we reported the average of the corresponding aspect ratios and number of crossings of the produced layouts. Note that all algorithms of the experiment can easily be adjusted to maximize only the crossing resolution, or only the angular resolution or both (by maximizing the total resolution). In our algorithm, this can be achieved by adjusting appropriately the content of the vertex-pool (as we saw in Section~\ref{ssec:variants}), while in the algorithms of Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13} and of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13} by switching on only the forces that maximize the corresponding properties under measure (note that, each of these two algorithms has a different set of forces to maximize the crossing and the angular resolution, such that together they maximize the total resolution).

\myparagraph{Crossing resolution} Our results for the crossing resolution are summarized in Fig.~\ref{fig:cr-res}. Here, each algorithm was adjusted to maximize exclusively the crossing resolution (i.e., by ignoring the drawing's angular resolution). It is immediate to see that our algorithm outperforms all other ones in terms of the crossing resolution of the produced drawings, when we do not impose any restriction on the aspect ratio of the computed drawings; refer to the solid-black curve, denoted as \emph{unrestricted}, in Fig.~\ref{fig:cr-res-1}. The variant of our algorithm, which does not violate the aspect ratio of the initial layout, leads to drawings with slightly smaller crossing resolution; refer to the solid-gray curve, denoted as \emph{ar-restricted}, in Fig.~\ref{fig:cr-res-1}. Finally, the two force-directed algorithms seem to produce drawings with worse crossing resolution; refer to the dotted-gray and dotted-black curves of Fig.~\ref{fig:cr-res-1} (by Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13} and by Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13}, respectively).

While our unrestricted algorithm produces drawings of better crossing resolution, this seems to come at a cost of drastically increased aspect ratio (see Fig.~\ref{fig:cr-res-2}), which, however, is still better that the corresponding aspect ratio of the drawings produced by the algorithm of Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13}. For the latter algorithm, it seems that the forces due to angles formed at the crossings outperform the corresponding spring forces, which try to keep the lengths of the edges short. Going back to our unrestricted algorithm, its behaviour is up to a certain degree expected mainly due to the fact that there is no control on the lengths of the edges.
% (as it is, e.g., in the case of the force-directed algorithm of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13}, whose sping forces inpose stong restrictions on the edge lengths). 
On the other hand, the restricted variant of our algorithm, which does not allow the aspect ratio to increase, has more or less comparable performace (in terms of the aspect ratio of the computed drawings) as the one of Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13}.
